Exploring Disparate Data: Part 1

### 2024-11-01 A3-Pt1.Rmd
np_cyclone All tests passed!

# Same steps as in A2, but you can put them all in the same pipeline!
at_cyclone <- str_c(cyclone_data_address, at_cyclone_filename, sep = "") |>
    read_csv(
        col_names = c(as.character(1:4)),
        progress = FALSE,
        show_col_types = FALSE
    ) |>
    filter(!grepl("AL", `4`)) |>
    separate_wider_delim(
        cols = `4`,
        # Set the delim and the names
        # YOUR CODE HERE
    ) |>
    mutate(
        across(everything(), str_trim),
        # make "-999" NAs, make "-99" NAs
        # Create columns BasinNumberYear, Name, and Entries
        across(everything(), ~na_if(., "-999")),
        across(everything(), ~na_if(., "-99")),
        BasinNumberYear = ifelse(is.na(status), `1`, NA),
        Name = ifelse(is.na(status), `2`, NA),
        Entries = ifelse(is.na(status), `3`, NA)
    ) |>
    relocate(BasinNumberYear, Name, Entries) |>
    fill(BasinNumberYear, Name, Entries) |>
    filter(!is.na(status))  |>
    select(-Entries) |>
    separate_wider_position(
        BasinNumberYear,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `1`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `2`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    rename(
        Identifier = `3`
    ) |>
    mutate(
        across(
            c(NameYear, ObservYear, Month, Day, Hour,
                Minute, Number),
            as.integer
        )
    ) |>
    mutate(across(max_wind:r_max_wind, as.numeric))

@@

```{r}
np_cyclone <- str_c(cyclone_data_address, np_cyclone_filename, sep = "") |>
    # ALL of the steps all over again
    # YOUR CODE HERE

print(np_cyclone)
```

>>>>

# Same steps as in A2, but you can put them all in the same pipeline!
at_cyclone <- str_c(cyclone_data_address, at_cyclone_filename, sep = "") |>
    read_csv(
        col_names = c(as.character(1:4)),
        progress = FALSE,
        show_col_types = FALSE
    ) |>
    separate_wider_delim(
        cols = `4`,
        delim = ",",
        names = new_columns
    ) |>
    mutate(
        across(everything(), str_trim),
        # make "-999" NAs, make "-99" NAs
        # Create columns BasinNumberYear, Name, and Entries
        across(everything(), ~na_if(., "-999")),
        across(everything(), ~na_if(., "-99")),
        BasinNumberYear = ifelse(is.na(status), `1`, NA),
        Name = ifelse(is.na(status), `2`, NA),
        Entries = ifelse(is.na(status), `3`, NA)
    ) |>
    relocate(BasinNumberYear, Name, Entries) |>
    fill(BasinNumberYear, Name, Entries) |>
    filter(!is.na(status))  |>
    select(-Entries) |>
    separate_wider_position(
        BasinNumberYear,
        # Specify the widths
        widths = c(Basin = 2, Number = 2, NameYear = 4)
    ) |>
    separate_wider_position(
        `1`,
        # Specify the widths
        widths = c(ObservYear = 4, Month = 2, Day = 2)
    ) |>
    separate_wider_position(
        `2`,
        # Specify the widths
        widths = c(Hour = 2, Minute = 2)
    ) |>
    rename(
        Identifier = `3`
    ) |>
    mutate(
        across(
            c(NameYear, ObservYear, Month, Day, Hour,
                Minute, Number),
            as.integer
        )
    ) |>
    mutate(across(max_wind:r_max_wind, as.numeric))

@@

```{r}
np_cyclone <- str_c(cyclone_data_address, np_cyclone_filename, sep = "") |>
    # ALL of the steps all over again
    read_csv(
        col_names = c(as.character(1:4)),
        progress = FALSE,
        show_col_types = FALSE
    ) |>
    separate_wider_delim(
        cols = `4`,
        delim = ",",
        names = new_columns
    ) |>
    mutate(
        across(everything(), str_trim),
        across(everything(), ~na_if(., "-999")),
        across(everything(), ~na_if(., "-99")),
        BasinNumberYear = ifelse(is.na(status), `1`, NA),
        Name = ifelse(is.na(status), `2`, NA),
        Entries = ifelse(is.na(status), `3`, NA)
    ) |>
    relocate(BasinNumberYear, Name, Entries) |>
    fill(BasinNumberYear, Name, Entries) |>
    filter(!is.na(status)) |>
    select(-Entries) |>
    separate_wider_position(
        BasinNumberYear,
        widths = c(Basin = 2, Number = 2, NameYear = 4)
    ) |>
    separate_wider_position(
        `1`,
        widths = c(ObservYear = 4, Month = 2, Day = 2)
    ) |>
    separate_wider_position(
        `2`,
        widths = c(Hour = 2, Minute = 2)
    ) |>
    rename(
        Identifier = `3`
    ) |>
    mutate(
        across(
            c(NameYear, ObservYear, Month, Day, Hour, Minute, Number),
            as.integer
        )
    ) |>
    mutate(across(max_wind:r_max_wind, as.numeric))

print(np_cyclone)
